DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-07-20 paper/paper.tex
do gamma math
fix transpose
full run code
fix paper

\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{t}^{I_{w_{jit}}=v}}{\sum_v \phi_{kt}}\]

@@

@@

\[= N(\text{\boldmath$\alpha$}_{i};\text{\boldmath$\alpha$}_{-1}^T \gamma_i, \delta^2)N(\eta, \xi^2)\]

@@

\[\Lambda_{\gamma i} = \left((\xi^2)^{-1} + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{-1}\right)^{-1}\]

\[\mu_{\gamma i} = \Lambda_{\gamma i} \left((\xi^2)^{-1} \eta + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{i}\right)\]

@@

Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.

@@

\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(w_{jkt}; \pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]

Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.

>>>>

\[= Mult\left(\left\{\frac{\theta_{kdit}}{\sum_{k'} \theta_{k'dit}}\frac{\phi_{kt}^{I_{w_{jit}}=v}}{\sum_v \phi_{kt}} \forall k \in K \right\}\right)\]

@@

Let $\Xi(x) = x^Tx$

\[p(\text{\boldmath$\alpha$}_i | \text{\boldmath$\alpha$}_{-1}, \gamma_i, \delta^2) = \prod_{t=2}^T p(\alpha_{it} | \alpha_{t-1}, \gamma_i, \delta^2)\]

\[= \frac{1}{\sqrt{2 \pi \delta^2}} \exp\left(-\frac{1}{2\delta^2} \sum_{t=2}^T \Xi\left(\alpha_{it} - \alpha_{t-1}^T \gamma_i\right)\right)\]

@@

\[\propto \exp\left(-\frac{1}{2 \delta^2} \sum_{t=2}^T \Xi\left(\alpha_{it} - \alpha_{t-1}^T \gamma_i\right)\right) \exp\left(-\frac{1}{2\xi^2}\Xi\left(\gamma_i - \eta\right)\right)\]

\[= \exp\left(-\frac{1}{2 \delta^2} \sum_{t=2}^T \left(\Xi(\alpha_{it}) + \Xi\left(\alpha_{t-1}^T \gamma_i\right) - 2 \alpha_{it}^T (\alpha_{t-1}^T \gamma_i) \right)\right) \exp\left(-\frac{1}{2\xi^2}\left(\Xi(\gamma_i) + \Xi(\eta) - 2 \gamma_i^T \eta)\right)\right)\]

\[= \exp\left(- \frac{\gamma_i^2}{2}\left(\frac{1}{\xi^2} + \frac{\Xi\left(\sum_{t=2}^T \alpha_{t-1}^T\right)}{\delta^2}\right) + \gamma_i \left(\frac{\eta}{\xi^2} + \frac{\left(\sum_{t=1}^T \alpha_{t-1}^T\right)^T \left(\sum_{t=2}^T \alpha_{it}\right)}{\delta^2}\right) - \left(\frac{\Xi(\eta)}{2\xi^2} + \frac{\Xi\left(\sum_{t=2}^T \alpha_{it}\right)}{2 \delta^2}\right)\right)\]

@@

\[\Lambda_{\gamma i} = \left(\frac{1}{\xi^2}+ \frac{\Xi\left(\sum_{t=2}^T \alpha_{t-1}^T\right)}{\delta^2}\right)^{-1}\]

\[\mu_{\gamma i} = \Lambda_{\gamma i} \left(\frac{\eta}{\xi^2} + \frac{\left(\sum_{t=1}^T \alpha_{t-1}^T\right)^T \left(\sum_{t=2}^T \alpha_{it}\right)}{\delta^2}\right)\]

@@

Since this doesn't have a standard form I use the method suggested by Minmo et. al\footnote{Mimno, Wallach and McCallum. Gibbs Sampling for Logistic Normal Topic Models with Graph-Based Priors. 2008.}.

@@

\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(w_{jkt}; \pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, \sigma^2)\]

Since this doesn't have a standard form I use the method suggested by Minmo et. al.
